Thesis Title

### 2022-05-24 chapters/chapter_4.tex
Updates from Overleaf

We have developed DEN-IM, a one-stop, user-friendly, containerised and reproducible workflow for the analysis of Dengue virus short-read sequencing data from both amplicon and shotgun metagenomics approaches. EN-IM was designed to perform a comprehensive analysis in order to generate either assemblies or consensus of full DENV coding sequences and to identify their serotype and genotype. DEN-IM can also detect all four DENV serotypes and the respective genotypes present in a spiked sample, raising the possibility that DEN-IM can play a role in the identification of co-infection cases whose prevalence is increasingly perceived in highly endemic areas.

>>>>

We have developed DEN-IM, a one-stop, user-friendly, containerised and reproducible workflow for the analysis of Dengue virus short-read sequencing data from both amplicon and shotgun metagenomics approaches. DEN-IM was designed to perform a comprehensive analysis in order to generate either assemblies or consensus of full DENV coding sequences and to identify their serotype and genotype. DEN-IM can also detect all four DENV serotypes and the respective genotypes present in a spiked sample, raising the possibility that DEN-IM can play a role in the identification of co-infection cases whose prevalence is increasingly perceived in highly endemic areas.

### 2022-05-24 chapters/chapter_8.tex
Updates from Overleaf

\begin{table}[]
\centering
\caption{Overview of testing approaches. Software testing can be separated into three types: installation, functionality and destructive. Each component is described, followed by an example on a real-life application on Software X, a hypothetical nucleotide sequence annotation tool}
\label{tab:ch8_table1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lll@{}}
\toprule
Name &
  Description &
  Example \\ \midrule
\multicolumn{3}{c}{\textbf{Installation testing: can the software be invoked on different setups?}} \\ \midrule
Installation testing &
  Can the software be installed on different platforms? &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X can be installed \\ using apt-get, pip, conda and from source.\end{tabular} \\
Configuration testing &
  With which dependencies can the software be used? &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X can be used \\ with different versions of blast+.\end{tabular} \\
Implementation testing &
  \begin{tabular}[c]{@{}l@{}}Do different implementations work \\ similarly enough?\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X works the same \\ between the standalone and webserver versions.\end{tabular} \\
Compatibility testing &
  \begin{tabular}[c]{@{}l@{}}Are newer versions compatible with \\ previous input/output?\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X can be used with \\ older versions of the UniProtKB database.\end{tabular} \\
Static testing &
  Is the source code syntactically correct? &
  \begin{tabular}[c]{@{}l@{}}Check whether all opening braces have \\ corresponding closing braces or whether \\ code is indented correctly in Software X.\end{tabular} \\ \midrule
\multicolumn{3}{c}{\textbf{Standard functionality testing: does the software do what it should in daily use?}} \\ \midrule
Use case testing &
  \begin{tabular}[c]{@{}l@{}}Can the software do what it is supposed to \\ do regularly?\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X can annotate different \\ FASTA files: with spaces in the header, \\ without a header, an empty file, with spaces in \\ the sequence, with unknown characters in the \\ sequences, et cetera.\end{tabular} \\
Workflow testing &
  \begin{tabular}[c]{@{}l@{}}Can the software successfully traverse each \\ path in the analysis?\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X works in different \\ modes (using fast mode or using one \\ dependency over the other).\end{tabular} \\
Sanity testing &
  Can the software be invoked without errors? &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X works correctly without \\ flags, or when checking dependencies or \\ displaying help info.\end{tabular} \\ \midrule
\multicolumn{3}{c}{\textbf{Destructive testing: what makes the software fail?}} \\ \midrule
Mutation testing &
  \begin{tabular}[c]{@{}l@{}}How do the current tests handle harmful \\ alterations to the software?\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Test whether changing a single addition to a \\ subtraction within Software X causes \\ the test suite to fail.\end{tabular} \\
Load testing &
  At what input size does the software fail? &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X can annotate a small \\ plasmid (10 kbp), a medium-size genome \\ (2 Mbp) or an unrealistically large \\ genome for a prokaryote (1 Gbp).\end{tabular} \\
Fault injection &
  \begin{tabular}[c]{@{}l@{}}Does the software fail if faults are introduced \\ and how is this handled?\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Test whether Software X fails if nonsense \\ functions are introduced in the gene calling code.\end{tabular} \\ \bottomrule
\end{tabular}%
}
\end{table}

@@

>>>>

\input{tables/chapter_8/table1}

@@

\begin{figure*}[]
\centering
\includegraphics[width=\textwidth]{figures/chapter 8/sup_fig_1.png}
\caption{Example YAML file for a GitHub Actions workflow.}
\label{fig:chap8_sup_figure1}
\end{figure*}

\input{tables/chapter_8/suptable1}

### 2022-05-24 tables/chapter_4/suptable2.tex
Updates from Overleaf

\begin{longtable}{@{}lllll@{}}
\caption{Run accession ID, BioProject SRA Study ID, source and organism present for each sample of the negative control dataset (ZKV – zika virus, CHIKV – chikungunya virus, YFV – yellow fever virus).}
\label{tab:chap4_s2}\\
\toprule
Run ID     & Bioproject  & SRA Study & Source                & Organism \\ \midrule

@@

SRR8261417 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV  \bottomrule   

@@

>>>>

\begin{scriptsize}
\begin{center}

\begin{longtable}{@{}lllll@{}}
\caption{Run accession ID, BioProject SRA Study ID, source and organism present for each sample of the negative control dataset (ZKV – zika virus, CHIKV – chikungunya virus, YFV – yellow fever virus).}
\label{tab:chap4_s2}\\

\toprule
\textbf{Run ID }    & \textbf{Bioproject}  & \textbf{SRA Study} & \textbf{Source} & \textbf{Organism} \\ \midrule
\endfirsthead

\multicolumn{5}{l}{\tablename \thetable - \textit{Continued from previous page} }\\
\toprule
\textbf{Run ID}     & \textbf{Bioproject}  & \textbf{SRA Study} & \textbf{Source} & \textbf{Organism} \\ \midrule
\endhead

\bottomrule
\multicolumn{5}{r}{\textit{Continue on next page}}\\
\endfoot

\bottomrule
\endlastfoot

@@

SRR8261417 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV    

@@

\end{center}
\end{scriptsize}

### 2022-05-24 tables/chapter_7/table1.tex
Updates from Overleaf

\begin{table}[h!]
\caption{Ontologies implemented in the PHA4GE SARS-CoV-2 specification.}
\label{tab:ch7_table1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}ll@{}}
\toprule
Ontology$^1$                                    & Link                                           \\ \midrule
BRENDA Tissue Ontology (BTO)                 & https://obofoundry.org/ontology/bto.html       \\
Cell Line Ontology (CLO)                     & https://obofoundry.org/ontology/clo.html       \\
Environmental conditions,   treatments and exposures ontology (ECTO) & https://obofoundry.org/ontology/ecto.html   \\
Environment Ontology (ENVO)                  & https://obofoundry.org/ontology/envo.html      \\
Food Ontology (FoodOn)                       & https://obofoundry.org/ontology/foodon.html    \\
Gazetteer Ontology (GAZ)                     & https://obofoundry.org/ontology/gaz.html       \\
Gender, Sex, and Sexual Orientation Ontology (GSSO)                  & https://obofoundry.org/ontology/gsso.html   \\
Genomic Epidemiology Ontology (GenEpiO)      & https://obofoundry.org/ontology/genepio.html   \\
Genomics Cohorts Knowledge Ontology (GECKO)  & https://obofoundry.org/ontology/gecko.html     \\
Human Disease Ontology (DOID)                & https://obofoundry.org/ontology/doid.html      \\
Human Phenotype Ontology (HP)                & https://obofoundry.org/ontology/hp.html        \\
Mammalian Phenotype Ontology (MP)            & https://obofoundry.org/ontology/mp.html        \\
Measurement Method Ontology (MMO)            & https://obofoundry.org/ontology/mmo.html       \\
Mondo Disease Ontology (MONDO)               & https://obofoundry.org/ontology/mondo.html     \\
Mouse Pathology Ontology (MPATH)             & https://obofoundry.org/ontology/mpath.html     \\
National Cancer Institute Thesaurus (NCIT)   & https://obofoundry.org/ontology/ncit.html      \\
NCBI Taxonomy Ontology (NCBITaxon)           & https://obofoundry.org/ontology/ncbitaxon.html \\
Neuro Behaviour Ontology (NBO)               & https://obofoundry.org/ontology/nbo.html       \\
Ontology for Biomedical Investigations (OBI) & https://obofoundry.org/ontology/obi.html       \\
Ontology of Medically Related Social Entities (OMRSE)                & https://obofoundry.org/ontology/omrse.html  \\
Population and Community Ontology (PCO)      & https://obofoundry.org/ontology/pco.html       \\
UBERON Multi-species Anatomy Ontology (UBERON)                       & https://obofoundry.org/ontology/uberon.html \\
Unit Ontology (UO)                           & https://obofoundry.org/ontology/uo.html        \\
Vaccine Ontology (VO)                        & https://obofoundry.org/ontology/vo.html        \\ \bottomrule
\end{tabular}%
}
\small
\item $^1$ Vocabulary for fields and terms in the specification have been sourced or mapped to OBO Foundry domain and application ontologies, which are highlighted in this list. New fields and terms for which there were no existing equivalents have been developed and submitted to these ontologies, expanding these community resources
\end{table}

>>>>

\begin{table}[h!]
\caption{Ontologies implemented in the PHA4GE SARS-CoV-2 specification.}
\label{tab:ch7_table1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Ontology}$^1$                                    & \textbf{Link}                                           \\ \midrule
BRENDA Tissue Ontology (BTO)                 & https://obofoundry.org/ontology/bto.html       \\
Cell Line Ontology (CLO)                     & https://obofoundry.org/ontology/clo.html       \\
Environmental conditions,   treatments and exposures ontology (ECTO) & https://obofoundry.org/ontology/ecto.html   \\
Environment Ontology (ENVO)                  & https://obofoundry.org/ontology/envo.html      \\
Food Ontology (FoodOn)                       & https://obofoundry.org/ontology/foodon.html    \\
Gazetteer Ontology (GAZ)                     & https://obofoundry.org/ontology/gaz.html       \\
Gender, Sex, and Sexual Orientation Ontology (GSSO)                  & https://obofoundry.org/ontology/gsso.html   \\
Genomic Epidemiology Ontology (GenEpiO)      & https://obofoundry.org/ontology/genepio.html   \\
Genomics Cohorts Knowledge Ontology (GECKO)  & https://obofoundry.org/ontology/gecko.html     \\
Human Disease Ontology (DOID)                & https://obofoundry.org/ontology/doid.html      \\
Human Phenotype Ontology (HP)                & https://obofoundry.org/ontology/hp.html        \\
Mammalian Phenotype Ontology (MP)            & https://obofoundry.org/ontology/mp.html        \\
Measurement Method Ontology (MMO)            & https://obofoundry.org/ontology/mmo.html       \\
Mondo Disease Ontology (MONDO)               & https://obofoundry.org/ontology/mondo.html     \\
Mouse Pathology Ontology (MPATH)             & https://obofoundry.org/ontology/mpath.html     \\
National Cancer Institute Thesaurus (NCIT)   & https://obofoundry.org/ontology/ncit.html      \\
NCBI Taxonomy Ontology (NCBITaxon)           & https://obofoundry.org/ontology/ncbitaxon.html \\
Neuro Behaviour Ontology (NBO)               & https://obofoundry.org/ontology/nbo.html       \\
Ontology for Biomedical Investigations (OBI) & https://obofoundry.org/ontology/obi.html       \\
Ontology of Medically Related Social Entities (OMRSE)                & https://obofoundry.org/ontology/omrse.html  \\
Population and Community Ontology (PCO)      & https://obofoundry.org/ontology/pco.html       \\
UBERON Multi-species Anatomy Ontology (UBERON)                       & https://obofoundry.org/ontology/uberon.html \\
Unit Ontology (UO)                           & https://obofoundry.org/ontology/uo.html        \\
Vaccine Ontology (VO)                        & https://obofoundry.org/ontology/vo.html        \\ \bottomrule
\end{tabular}%
}
\small
\item $^1$ Vocabulary for fields and terms in the specification have been sourced or mapped to OBO Foundry domain and application ontologies, which are highlighted in this list. New fields and terms for which there were no existing equivalents have been developed and submitted to these ontologies, expanding these community resources
\end{table}

### 2022-05-24 tables/chapter_7/table2.tex
Updates from Overleaf

Resource$^1$ &
  Description \\

@@

  \begin{tabular}[c]{@{}l@{}}Javascript application enabling standardized data entry, validation and \\ export of contextual data as submission-ready forms for GISAID and \\ NCBI. The SOP for using the software can be found at \\ https://github.com/Public-Health-Bioinformatics/\\ DataHarmonizer/wiki/PHA4GE-SARS-CoV-2-Template\end{tabular}  

>>>>

\textbf{Resource}$^1$ &
  \textbf{Description} \\

@@

  \begin{tabular}[c]{@{}l@{}}Javascript application enabling standardized data entry, validation and \\ export of contextual data as submission-ready forms for GISAID and \\ NCBI. The SOP for using the software can be found at \\ https://github.com/Public-Health-Bioinformatics/\\ DataHarmonizer/wiki/PHA4GE-SARS-CoV-2-Template\end{tabular} \\

### 2022-05-24 tables/chapter_7/table3.tex
Updates from Overleaf

\small

\begin{longtable}[c]{@{}lll@{}}
\caption{Minimal (required) contextual data fields. Through consultation and consensus, fourteen fields were prioritized for SARS-CoV-2 surveillance, which are considered required in the specification. Field names, definitions, and guidance are presented.}
\label{tab:ch7_table3}\\ 
\toprule
Field   Name &
  Definition &
  Guidance \\ \midrule
\endfirsthead
%
\endhead
%

@@

  \begin{tabular}[c]{@{}l@{}}Every Sample ID from a single submitter must\\ be unique. It can have any format, but we \\ suggest that you make it concise, \\ unique and consistent within your lab, \\ and as informative as possible.\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}The name of the agency should be written out\\ in full, (with minor exceptions) and consistent \\ across multiple submissions.\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}The name of the agency should be written out\\ in full, (with minor exceptions) and be \\ consistent across multiple submissions.\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}Record the collection date accurately in the \\ template. Required granularity includes year, \\ month and day. Before sharing this data, \\ ensure this date is not considered identifiable \\ information. If this date is considered identifiable, \\ it is acceptable to add "jitter" to the collection date \\ by adding or subtracting calendar days. Do not \\ change the collection date in your original records. \\ Alternatively,” received date” may be used as a \\ substitute in the data you share. The date should be \\ provided in ISO 8601 standard format \\ "YYYY-MM-DD".\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}Provide the country name from the pick list\\ in the template.\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}Provide the state/province/region name from\\ the GAZ geography ontology. Search for geography \\ terms here: https://www.ebi.ac.uk/ols/ontologies/gaz\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}Use “Severe acute respiratory \\ syndrome coronavirus 2”\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}This identifier should be an unique, indexed, \\ alpha-numeric ID within your laboratory. If \\ submitted to the INSDC,  the "isolate" name \\ is propagated throughout different databases. \\ As such, structure the "isolate" name to be \\ ICTV/INSDC compliant in the following format: \\ "SARS-CoV-2/host/country/sampleID/date"\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}Common name or scientific name are required \\ if there was a host. Scientific name examples \\ e.g., Homo sapiens. Select a value from the \\ pick list. If the sample was environmental, \\ put "not applicable".\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}This field is only required if there was a\\ host. If the host was a human select COVID-19\\ from the pick list. If the host was asymptomatic, \\ this can be recorded under “host health state details”. \\ "COVID-19" should still be provided if the patient \\ is asymptomatic. If the host is not human, and the\\ disease state is not known or the host appears \\ healthy, put “not applicable”.\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}The reason why a sample was originally\\ collected may differ from the reason\\ why it was selected for sequencing. The\\ reason a sample was sequenced may \\ provide information about potential biases \\ in sequencing strategy. Provide the \\ purpose of sequencing from the picklist \\ in the template. The reason for sample \\ collection should be indicated in the  \\ "purpose of sampling" field.\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}Select a sequencing instrument from the \\ picklist provided in the template.\end{tabular} \\

@@

  \begin{tabular}[c]{@{}l@{}}Provide the name of the software used to\\ generate the consensus sequence.\end{tabular} \\

@@

\normalsize

>>>>

\begin{scriptsize}
\begin{center}

\begin{longtable}[c]{@{}lll@{}}
\caption{Minimal (required) contextual data fields. Through consultation and consensus, fourteen fields were prioritized for SARS-CoV-2 surveillance, which are considered required in the specification. Field names, definitions, and guidance are presented.}
\label{tab:ch7_table3}\\ 
\toprule
\textbf{Field   Name} &
  \textbf{Definition} &
  \textbf{Guidance} \\ \midrule
\endfirsthead

\multicolumn{3}{l}{\tablename \thetable - \textit{Continued from previous page} }\\
\toprule
\textbf{Field   Name} &
  \textbf{Definition} &
  \textbf{Guidance} \\ \midrule
\endhead

\bottomrule
\multicolumn{3}{r}{\textit{Continue on next page}}\\
\endfoot

\bottomrule
\endlastfoot

@@

  \begin{tabular}[c]{@{}l@{}}Every Sample ID from a single submitter must\\ be unique. It can have any format, but we \\ suggest that you make it concise, \\ unique and consistent within your lab, \\ and as informative as possible.\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}The name of the agency should be written out\\ in full, (with minor exceptions) and consistent \\ across multiple submissions.\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}The name of the agency should be written out\\ in full, (with minor exceptions) and be \\ consistent across multiple submissions.\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}Record the collection date accurately in the \\ template. Required granularity includes year, \\ month and day. Before sharing this data, \\ ensure this date is not considered identifiable \\ information. If this date is considered identifiable, \\ it is acceptable to add "jitter" to the collection date \\ by adding or subtracting calendar days. Do not \\ change the collection date in your original records. \\ Alternatively,” received date” may be used as a \\ substitute in the data you share. The date should be \\ provided in ISO 8601 standard format \\ "YYYY-MM-DD".\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}Provide the country name from the pick list\\ in the template.\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}Provide the state/province/region name from\\ the GAZ geography ontology. Search for geography \\ terms here: https://www.ebi.ac.uk/ols/ontologies/gaz\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}Use “Severe acute respiratory \\ syndrome coronavirus 2”\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}This identifier should be an unique, indexed, \\ alpha-numeric ID within your laboratory. If \\ submitted to the INSDC,  the "isolate" name \\ is propagated throughout different databases. \\ As such, structure the "isolate" name to be \\ ICTV/INSDC compliant in the following format: \\ "SARS-CoV-2/host/country/sampleID/date"\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}Common name or scientific name are required \\ if there was a host. Scientific name examples \\ e.g., Homo sapiens. Select a value from the \\ pick list. If the sample was environmental, \\ put "not applicable".\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}This field is only required if there was a\\ host. If the host was a human select COVID-19\\ from the pick list. If the host was asymptomatic, \\ this can be recorded under “host health state details”. \\ "COVID-19" should still be provided if the patient \\ is asymptomatic. If the host is not human, and the\\ disease state is not known or the host appears \\ healthy, put “not applicable”.\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}The reason why a sample was originally\\ collected may differ from the reason\\ why it was selected for sequencing. The\\ reason a sample was sequenced may \\ provide information about potential biases \\ in sequencing strategy. Provide the \\ purpose of sequencing from the picklist \\ in the template. The reason for sample \\ collection should be indicated in the  \\ "purpose of sampling" field.\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}Select a sequencing instrument from the \\ picklist provided in the template.\end{tabular} \\ \midrule

@@

  \begin{tabular}[c]{@{}l@{}}Provide the name of the software used to\\ generate the consensus sequence.\end{tabular} \\ \midrule

@@

\end{center}
\end{scriptsize}

### 2022-05-24 tables/chapter_7/table4.tex
Updates from Overleaf

\begin{table}[]
\centering
\caption{A selection of accession numbers of harmonized contextual data records submitted to different public repositories.}
\label{tab:ch7_table4}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lll@{}}
\toprule
Data   Contributor &
  Repository   Name &
  Accession   Number \\ \midrule
\begin{tabular}[c]{@{}l@{}}African Centre of Excellence for Genomics \\ of Infectious Diseases (Nigeria)\end{tabular} &
  GISAID &
  \begin{tabular}[c]{@{}l@{}}EPI\_ISL\_1035827\\ EPI\_ISL\_1035826\\ EPI\_ISL\_1035825\end{tabular} \\ \midrule
\begin{tabular}[c]{@{}l@{}}COVID-19 Genomic Surveillance \\ Regional Network (Latin America)\end{tabular} &
  GISAID &
  \begin{tabular}[c]{@{}l@{}}EPI\_ISL\_2158821\\ EPI\_ISL\_2158802\\ EPI\_ISL\_2158810\end{tabular} \\ \midrule
\begin{tabular}[c]{@{}l@{}}COVID-19 Genomic Surveillance \\ Regional Network (Latin America)\end{tabular} &
  EMBL-EBI &
  SAMEA8968916 \\ \midrule
\begin{tabular}[c]{@{}l@{}}Rhode Island Department of \\ Health/Broad Institute (SPHERES)\end{tabular} &
  NCBI &
  SAMN18306978 \\ \midrule
\begin{tabular}[c]{@{}l@{}}Massachusetts General Hospital/Broad\\ Institute (SPHERES)\end{tabular} &
  NCBI &
  SAMN18309294 \\ \midrule
Flow Health/Broad Institute (SPHERES) &
  NCBI &
  SAMN18308763 \\ \midrule
\begin{tabular}[c]{@{}l@{}}New Brunswick Diagnostic Virology Reference\\ Center/Public Health Agency of Canada (CanCOGeN)\end{tabular} &
  NCBI &
  SAMN16784832 \\ \midrule
\begin{tabular}[c]{@{}l@{}}Toronto Invasive Bacterial Diseases \\ Network/McMaster University (CanCOGeN)\end{tabular} &
  NCBI &
  SAMN17505317 \\ \midrule
\begin{tabular}[c]{@{}l@{}}Bat coronavirus phylogeography- Université de La Réunion, \\ UMR Processus Infectieux en Milieu Insulaire Tropical (PIMIT) \\ and Field Museum of Natural History\end{tabular} &
  NCBI &
  \begin{tabular}[c]{@{}l@{}}SAMN20400589\\ SAMN20400588\end{tabular}
\end{tabular}%
}
\end{table}

>>>>

\begin{table}[]
\centering
\caption{A selection of accession numbers of harmonised contextual data records submitted to different public repositories.}
\label{tab:ch7_table4}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Data   Contributor} &
  \textbf{Repository   Name} &
  \textbf{Accession   Number} \\ \midrule
\begin{tabular}[c]{@{}l@{}}African Centre of Excellence for Genomics \\ of Infectious Diseases (Nigeria)\end{tabular} &
  GISAID &
  \begin{tabular}[c]{@{}l@{}}EPI\_ISL\_1035827\\ EPI\_ISL\_1035826\\ EPI\_ISL\_1035825\end{tabular} \\ \midrule
\begin{tabular}[c]{@{}l@{}}COVID-19 Genomic Surveillance \\ Regional Network (Latin America)\end{tabular} &
  GISAID &
  \begin{tabular}[c]{@{}l@{}}EPI\_ISL\_2158821\\ EPI\_ISL\_2158802\\ EPI\_ISL\_2158810\end{tabular} \\ \midrule
\begin{tabular}[c]{@{}l@{}}COVID-19 Genomic Surveillance \\ Regional Network (Latin America)\end{tabular} &
  EMBL-EBI &
  SAMEA8968916 \\ \midrule
\begin{tabular}[c]{@{}l@{}}Rhode Island Department of \\ Health/Broad Institute (SPHERES)\end{tabular} &
  NCBI &
  SAMN18306978 \\ \midrule
\begin{tabular}[c]{@{}l@{}}Massachusetts General Hospital/Broad\\ Institute (SPHERES)\end{tabular} &
  NCBI &
  SAMN18309294 \\ \midrule
Flow Health/Broad Institute (SPHERES) &
  NCBI &
  SAMN18308763 \\ \midrule
\begin{tabular}[c]{@{}l@{}}New Brunswick Diagnostic Virology Reference\\ Center/Public Health Agency of Canada (CanCOGeN)\end{tabular} &
  NCBI &
  SAMN16784832 \\ \midrule
\begin{tabular}[c]{@{}l@{}}Toronto Invasive Bacterial Diseases \\ Network/McMaster University (CanCOGeN)\end{tabular} &
  NCBI &
  SAMN17505317 \\ \midrule
\begin{tabular}[c]{@{}l@{}}Bat coronavirus phylogeography- Université de La Réunion, \\ UMR Processus Infectieux en Milieu Insulaire Tropical (PIMIT) \\ and Field Museum of Natural History\end{tabular} &
  NCBI &
  \begin{tabular}[c]{@{}l@{}}SAMN20400589\\ SAMN20400588\end{tabular} \\ \midrule
\end{tabular}%
}
\end{table}
